\usepackage{hyperref}%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}


  \cventry
  {C++}
  {finman}
  {\href{https://github.com/UnciaBit/finman}{GitHub}} % Location
  {Jan. 2022 - PRESENT}
  {
    \begin{cvitems}
      \item {Command-line finance manager built using C++}
      \item {Uses SQLite as a database}
    \end{cvitems}
  }

  \cventry
  {C}
  {Sequence Analyser}
  {\href{https://github.com/UnciaBit/Sequence-Analysis}{GitHub}} % Location
  {Jan. 2022 - PRESENT}
  {
    \begin{cvitems}
      \item {Simple and fast Sequence analysis tool (DNA/RNA) based on Aho-Corasick algorithm}
      \item {Inputs a sequence and a pattern, outputs the number of occurrences of the pattern in the sequence}
    \end{cvitems}
  }



  \cventry
  {NodeJS, Javascript, Redis}
  {UnciaNet}
  {\href{https://github.com/UnciaBit/UnciaNet-FE}{GitHub}} % Location
  {Dec. 2021 - PRESENT}
  {
    \begin{cvitems}
      \item {Fully featured Blockchain network with NodeJS and Redis backend}
      \item {REST API made for creating transactions}
      \item {Currently under development to transform into blockchain visualisation/learning tool}
    \end{cvitems}
  }


%---------------------------------------------------------
  \cventry
    {Rust} 
    {KeySort} 
    {\href{https://github.com/UnciaBit/KeySort-cli}{GitHub}, \href{https://crates.io/crates/keysort}{Cargo}} % Location
    {Nov. 2021 - PRESENT} 
    {
      \begin{cvitems}
        \item {Small command-line utility to sort files and folders into character assigned folders}
        \item {Built efficiently with Rust}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {PHP, HTML, CSS, Javascript, MySQL} 
    {EqManage} 
    {\href{https://github.com/YukiKume/EqManage}{GitHub}} % Location
    {Oct. 2019 - Jan. 2021} 
    {
      \begin{cvitems}
        \item {Client: Dulwich College Suzhou}
        \item {Equpment (Renting) management system}
        \item {Users can rent equipment, set renting period + message. Admins can approve or deny the request. Includes dashoard, overdue tracking etc...}
        \item (With MySQL as a database and PHP + Javascript for backend)
      \end{cvitems}
    }

  \cventry
  {POEdit, PHP, CSS, Javascript, HTML}
  {cocoon}
  {\href{https://github.com/WrenHainsworth/cocoon}{GitHub}} % Location
  {Oct 2021 - Present}
  {
    \begin{cvitems}
      \item {Fork of yhira/cocoon}
      \item {SEO optimised WordPress theme}
      \item {Mainly contributed the translation that was then pushed to the official branch in the main repository}
      \item {Few tweaks made to the theme for personal use}
    \end{cvitems}
  }


  \cventry
  {C$\sharp$ (Unity), Cinema 4D} 
  {Tower defense game} 
  {} % Location
  {Jan. 2018} 
  {
    \begin{cvitems}
      \item {Tower Defense Game built using Unity}
      \item {Single player game, where the player defends endpoint from incoming enemies. All elements including the tower design were solo developed}
    \end{cvitems}
  }

  \cventry
  {PHP, MySQL, HTML, CSS, Javascript} 
  {Chatbox} 
  {} % Location
  {Jul. 2016} 
  {
    \begin{cvitems}
      \item {Chatroom where multiple users can chat with each other, with online status, and chat history. Similar to Discord}
    \end{cvitems}
  }

%---------------------------------------------------------
\end{cventries}
